Localisation and Sensor Privacy Using the Extended Information Filter and Private Linear-Combination Aggregation\thanksref{footnoteinfo}

### 2020-09-10 main.tex
EIF section just about done, last sentence missing

The navigator state is defined as 
\begin{equation}
    \vec{x} = 
    \begin{bmatrix}
        x & dx & y & dy
    \end{bmatrix}^\top\,.
\end{equation}
A known process model is followed, which at time $k$ is given by
\begin{equation}
    \mean{x}_k = f(\mean{x}_{k-1})+\rvec{w}_k\,, \label{eqn:process_model}
\end{equation}
with zero-mean Gaussian process noise $w_k \sim \mathcal{N}(\vec{0},\mat{Q})$. The measurement model is dependant on sensor $i$ and given by
\begin{equation}
    z_k = h_i(\mean{x}_k)+\rv{v}_k\,, \label{eqn:measurement_model}
\end{equation}
with noise $\rv{v}_k \sim \mathcal{N}(\vec{0},\mat{R})$, while the measurement function $h_i$, for sensor $i$ at location
\begin{equation}
    \vec{s}_i = 
    \begin{bmatrix}
        x_{i} & y_{i}
    \end{bmatrix}^\top\,,
\end{equation} 
is defined as
\begin{equation}
    \begin{split}
        h_i(\mean{x}_k) &= \left\|
        \begin{bmatrix}
            \mean{x}_{k[0]} \\
            \mean{x}_{k[2]}
        \end{bmatrix}
        - \vec{s}_{i}\right\| \\
        &= \sqrt{(\mean{x}_{k[0]}-x_{i})^2 + (\mean{x}_{k[2]}-y_{i})^2}\,.
    \end{split}
\end{equation}
We wish to run a state estimation filter with models \eqref{eqn:process_model} and \eqref{eqn:measurement_model} such that all involved sensors $1 \leq i \leq n$ do not learn the estimated state $\mean{x}_k$ and the navigator does not learn sensor locations $\vec{s}_i,\,1 \leq i \leq n$ or their measurements $z_k$ at any time $k$.

@@

\subsection{Extended Information Filter}
EIF is a reformulation of the EKF where the update step is reduced to sums. Makes it especially easier for processing multiple measurements.

Prediction step can be computed in either the EIF form or the equivalent EKF state and covariance can be computed before performing the prediction step in EKF form and converting the result back.

% The Extended Information Filter (EIF) is an algebraic reformulation of the Extended Kalman Filter (EKF) such that the update step is reduced to a simple summation. Given process and measurement models \eqref{} and \eqref{}, the EIF update equation is given by
% \begin{equation}
%     a
% \end{equation}

>>>>

The navigator state is defined as 
\begin{equation}
    \vec{x} = 
    \begin{bmatrix}
        x & dx & y & dy
    \end{bmatrix}^\top\,.
\end{equation}
A known process model is followed, which at time $k$ is given by
\begin{equation}
    \mean{x}_k = \vec{f}(\mean{x}_{k-1})+\rvec{w}_k\,, \label{eqn:process_model}
\end{equation}
with zero-mean Gaussian process noise $w_k \sim \mathcal{N}(\vec{0},\mat{Q})$. The measurement model is dependant on sensor $i$ and given by
\begin{equation}
    z_k = h_i(\mean{x}_k)+\rv{v}_k\,, \label{eqn:measurement_model}
\end{equation}
with noise $\rv{v}_k \sim \mathcal{N}(\vec{0},\mat{R})$, while the measurement function $h_i$, for sensor $i$ at location
\begin{equation}
    \vec{s}_i = 
    \begin{bmatrix}
        x_{i} & y_{i}
    \end{bmatrix}^\top\,,
\end{equation} 
is defined as
\begin{equation}
    \begin{split}
        h_i(\mean{x}_k) &= \left\|
        \begin{bmatrix}
            \mean{x}_{k[0]} \\
            \mean{x}_{k[2]}
        \end{bmatrix}
        - \vec{s}_{i}\right\| \\
        &= \sqrt{(\mean{x}_{k[0]}-x_{i})^2 + (\mean{x}_{k[2]}-y_{i})^2}\,.
    \end{split}
\end{equation}
We wish to run a state estimation filter with models \eqref{eqn:process_model} and \eqref{eqn:measurement_model} such that all involved sensors $1 \leq i \leq n$ do not learn the estimated state $\mean{x}_k$ and the navigator does not learn sensor locations $\vec{s}_i,\,1 \leq i \leq n$ or their measurements $z_k$ at any time $k$.

@@

\subsection{Extended Information Filter}
Given process and measurement models \eqref{eqn:process_model} and \eqref{eqn:measurement_model}, the Extended Information Filter (EIF) is a reformulation of the Extended Kalman Filter (EKF), such that the update equations are simpified to sums of measurement information from each sensor. This requires the conversion of state estimate $\mean{x}_k$ and estimate covariance $\mat{P}_k$ to the information vector and matrix forms
\begin{equation}
    \mean{y}_k = \mat{P}_k^{-1}\mean{x}_k
\end{equation}
and
\begin{equation}
    \mat{Y}_k = \mat{P}_k^{-1}\,.
\end{equation}
In this form, the update equations for $n$ measurements at time $k$ are given by
\begin{equation}
    \mat{Y}_k = \mat{Y}_{k-1} + \sum^n_{i=1}\mat{H}^\top_{k,i} \mat{R}^{-1}_i \mat{H}_{k,i}
\end{equation}
and
\begin{equation}
    \mean{y}_k = \mean{y}_{k-1} + \sum^n_{i=1}\mat{H}^\top_{k,i} \mat{R}^{-1}_i (z_{k,i} - h_i(\mean{x}_k) + \mat{H}_{k,i}\mean{x}_k)\,,
\end{equation}
with Jacobian
\begin{equation}
    \mat{H}_{k,i} = \left.\frac{\partial h_i}{\partial \vec{x}}\right|_{\mean{x}_k}
\end{equation}
for each sensor $1 \leq i \leq n$.

Computing the prediction step of the filter can be done by converting the information vector and matrix back to state estimate and covariance with
\begin{equation}
    \mat{P}_k = \mat{Y}_k^{-1}
\end{equation}
and
\begin{equation}
    \mean{x}_k = \mat{P}_k\mean{y}_k\,,
\end{equation}
and using the normal EKF prediction equations

%Prediction step can be computed in either the EIF form or the equivalent EKF state and covariance can be computed before performing the prediction step in EKF form and converting the result back.
